My title

### 2024-03-29 paper/paper.qmd
adjust graph

posterior_vs_prior(poverty_prediction_model) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

posterior_vs_prior(poverty_prediction_model, size = 0.3) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  theme(axis.text.x=element_text(hjust=1, vjust=0.5),
        text=element_text(size=8)) +
  guides(color = guide_legend(ncol = 3))+
  coord_flip()
```
